Preprocessing and exploration of the narwhal data for the analysis with smoothSDE

### 2024-05-08 R/preprocessing/data_preprocessing.Rmd
changes in preprocessing for land

#get land polygons
modified_land_utm<-st_read(file.path(greenland_data_path,"modified_land_utm.shp"))
modified_land_utm <- st_transform(modified_land_utm, crs = "+init=EPSG:32626 +units=km")

@@

```{r plot coastline and land}
plot_land=ggplot()+geom_sf(data=land_utm$geometry,fill="grey",col="brown")+
  coord_sf(datum=st_crs(32626))
plot_modified_land=ggplot()+geom_sf(data=modified_land_utm$geometry,fill="grey",col="blue")+
  coord_sf(datum=st_crs(32626))
plot_land_google=ggplot()+geom_sf(data=land_google_utm$geometry,fill="grey",col="blue")+
  coord_sf(datum=st_crs(32626))
```

@@

```{r summary distances to shore}
summary(res_land$min_distances)
summary(dataprep$DistanceShore)
```

@@

cat("Percentage of points on land with distance from modified : \n",
    length(which(res_modified_land$min_distances==0))/length(dataprep$time)*100)
```

>>>>

@@

```{r plot coastline and land}
plot_land=ggplot()+geom_sf(data=land_utm$geometry,fill="grey",col="brown")+
  coord_sf(datum=st_crs(32626))

plot_land_google=ggplot()+geom_sf(data=land_google_utm$geometry,fill="grey",col="blue")+
  coord_sf(datum=st_crs(32626))
```

@@

```{r summary distances to shore}
summary(res_land$min_distances)
summary(dataprep$DistanceShore)
quantile(res_land$min_distance,probs=c(0.05,0.95))
```

@@
